\documentclass[12pt]{report}
\input{doc_struct/packages}
\input{doc_struct/definitions}
\input{doc_struct/latex_config}
\input{doc_struct/author_committee}

%\title{Index for Relational Hierarchical Structures and A Case Study of Migration from MySQL to MongoDB (Draft)}
%\title{Hierarchical and Spatial Indexing in Scientific Database}

%\title{Index Structures for Hierarchical, Spatial, and Unstructured Data in Scientific and Dusty Plasma Physics Database}

\title{Database Indexing for Skyline Computation, Hierarchical Relational Database, and Spatially-Aware SPARQL Evaluation Engine}

\begin{document}

\begin{romanpages}      % roman-numbered pages 

\TitlePage 

\begin{abstract}
Computer databases are ubiquitous and play an important role in many software projects. The efficiency of these systems are crucial in applications they support. Data indexing is the key to efficient data retrieval in database systems. This dissertation considers three data application domains and operations in which data indexing can greatly improve the turnaround time of request operations.

The first part is the study of multi-dimensional and multi-criteria skyline computation. Skyline is a subset of data records that are the best in a data set, where best is defined by user criteria and preference. In our technique, we first create an index using the R-Tree structure. We then propose a greedy algorithm that utilizes the R-Tree index to aggressively prune the search space as the index is traversed. Experimental evaluation shows that our algorithm performs better than previous algorithms.

In the second part of this dissertation, we consider the efficiency of querying hierarchical data in a relational database (hierarchical relational database). The relational database model is known to efficiently store and retrieve data stored in flat tables; however, it was not designed for hierarchical data. Due to this limitation, many operations -- such as answering membership on a hierarchical data -- require recursion or iterations. In this study, we propose an index structure based on the nested-sets model. With this index, we can eliminate recursions and allow database engines to perform hierarchical operations with index scans.

In the last part of this dissertation, we consider storage and retrieval of point-based spatial data (POIs) in the Geo-Store RDF triple store. When we first started this study, spatial data management in RDF was still a fairly new research area and there were no standard for query spatial data using SPARQL. In this work, we designed an index scheme using the Hilbert Space-Filing Curve (HSFC). Leveraging the spatial locality of HSFC, we are able to efficiently evaluate spatial queries such as range and k-nearest-range (kNN) queries. In this work, we define range and kNN SPARQL filters. We implemented there filters and showed that our implementation handles spatial queries better than other triple stores.
\end{abstract}

\begin{acknowledgments}

I would first like to thank my advisory committee for the guidance and support.
I want to thank my advisor, Dr. Wei-Shinn Ku, for his guidance and mentoring throughout my graduate studies. His expertise in the fields of spatial database management has facilitated my research and the completion of my dissertation. This dissertation would not be possible without his insight.

I want to express my gratitude to my advisory committee member, Dr. James Cross, whose careful review of this dissertation and expertise of technical writing made this dissertation as good as it can be. His character of excellence has propelled me to strive for excellence in my work.

I would like to thank my advisory committee member, Dr. Xiao Qin, for helping me to revise this dissertation. I am especially thankful for his suggestions in correcting logical and grammatical errors in early drafts. In addition, I also want to thank him for career advice.

I am thankful for the advice and words of encouragement of my advisory committee member, Dr. Alvin Lim. His knowledge in semantic web and related works has offered a unique perspective to ensure the quality of this dissertation.

I want to especially thank Dr. Edward Thomas, Jr. for serving as the University Reader of my advisory committee. I am grateful for the discussions we had during my graduate study and his support for me to finish my degree.

I want to give special thanks to my parents and my family for the unwavering support to help me pursue my degree. I would not be able to complete this dissertation without their support.
\end{acknowledgments}

\tableofcontents
\listoffigures
\listoftables
%\printnomenclature[0.5in] %used for the List of Abbreviations
\end{romanpages}        % All done with roman-numbered pages


%\normalem       % Make italics the default for \em

\chapter{Efficient Evaluation of Skyline Queries in Wireless Data Broadcast Environments}
\import{bsky/}{BSky}

\chapter{Computerized Control and Data Acquisition System for MDPX}
\import{mdpx/}{body}

\chapter{Hierarchical Data in Relational Database Management Systems}
\import{reltree-paper/text/}{body}

%\chapter{A Case Study of Migration from MySQL to MongoDB}
%\import{mongodb/}{body}

\chapter{Geo-Store: A Spatially-Aware SPARQL Evaluation Engine}
\input{geo-store-journal/chapter}

%\input{schedule/text.tex}

%\bibliographystyle{plain}
%\bibliography{mdpx/ref}


\bibliographystyle{plain}
\bibliography{mdpx/bib/ref,mdpx/bib/cmod,mdpx/bib/mdsplus,mdpx/bib/d3d,mdpx/bib/lhd,mdpx/bib/nstx,mdpx/bib/w7x,mdpx/bib/iter,mdpx/bib/demo,mdpx/bib/epics,mdpx/bib/labview,reltree-paper/text/bib,bib,mongodb/bib}
\end{document}

