\chapter{Tasks and Schedule}

\section{Tasks}

\subsection{Hierarchical Data in Relational Database Management Systems}

For our work on hierarchical date index, we have already explored related works, and studied the theoretical background that supports our design. In additional to the work we have done, the following are the work still to be done.

\begin{enumerate}
\item Design experiments to evaluate the efficiency of our design.
\item Implement experiments.
\item Report experimental results and finalize paper.
\end{enumerate}


\subsection{Efficient Evaluation of Skyline Queries}

For this work, we are exploring a new algorithm for evaluating skyline operations. Specifically we are exploring an algorithm based on the Branch and Bound Skyline (BBS). With out algorithm, we aim to improve the memory and the speed over BBS. The following are the task items.

\begin{enumerate}
\item Research into new skyline algorithm.
\item Design and conduct experiments.
\item Report experimental results.
\end{enumerate}

\subsection{Moving Toward Semantic Web Database}

The follow are the task items.

\begin{enumerate}
\item Study benefit of using semantic web technology.
\item Alternatives to semantic web.
\item Design experimental database.
\item Report results.
\end{enumerate}

\section{Schedule}

\begin{table}[ht]
\centering
\begin{tabular}{|l|l|l|}
\hline
{\bf Tasks} & {\bf Duration} & {\bf Completion Date} \\ \hline\hline
Research Proposal Defense & 4 weeks & July 31, 2013 \\
Experimental evaluation for hierarchical data index & 4 weeks & August 31, 2013 \\
Finalize hierarchical index design & 2 weeks & September 16, 2013\\
Finalize report for hierarchical index & 2 weeks & September 30, 2013\\
Design experiment and evaluation & 8 weeks & November 30, 2013 \\
Study semantic web and RDF technology & 4 weeks & December 31, 2013\\
Design Experiment and RDF database & 8 weeks & February 28, 2014\\
Design evaluation & 4 weeks & March 31, 2014\\
Finalize dissertation & 8 weeks & May 2014\\
\hline
\end{tabular}
%\caption{Common operation Examples\label{table:common_operation_examples}}
\end{table}